Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-04 docs/Villasenor-Derbez.Rmd
Moved all manuscript files one level up into docs

The model interpretation remains as for Eq \ref{eqn:reg_bio}, but in this case the $Treated$ dummy variable indicates if the community has a reserve ($Treated = 1$) or not ($Treated = 0$) and $\sigma_jCom$ captures community-level fixed-effects. These regression models allow us to establish a causal link between the implementation of marine reserves and the observed trends by accounting for temporal and spatial dynamics \citep{depalma_2018}. The effect of the reserve is captured by the $\lambda_t$ coefficient, and represents the difference observed between the control site before the implementation of the reserve and the treated sites at time $t$ after controlling for other time and space variations (*i.e.* $\gamma_t$ and $\beta$ respectively). All model coefficients were estimated via ordinary least-squares and heteroskedastic-robust standard errors \citep{zeileis_2004-7n}. All analyses were performed in `r version$version.string` and R Studio version 1.1.456 \citep{R_2018}.

>>>>

The model interpretation remains as for Eq \ref{eqn:reg_bio}, but in this case the $Treated$ dummy variable indicates if the community has a reserve ($Treated = 1$) or not ($Treated = 0$) and $\sigma_jCom$ captures community-level fixed-effects. These regression models allow us to establish a causal link between the implementation of marine reserves and the observed trends by accounting for temporal and spatial dynamics \citep{depalma_2018}. The effect of the reserve is captured by the $\lambda_t$ coefficient, and represents the difference observed between the control site before the implementation of the reserve and the treated sites at time $t$ after controlling for other time and space variations (*i.e.* $\gamma_t$ and $\beta$ respectively). All model coefficients were estimated via ordinary least-squares and heteroskedastic-robust standard errors \citep{zeileis_2004-7n}. All analyses were performed in R `r paste0("version ", version$major, ".", version$minor)` and R Studio version 1.1.456 \citep{R_2018}. All data and code ara available in a [GitHub repository](https://github.com/jcvdav/ReserveEffect).
